\section{Extra Curricular}
  \resumeSubHeadingListStart
  \resumeSubheading
    {Executive of Finanace Team}{September 2024 - Present}
    {Association of Korean Canadian Scientists and Engineers}{Waterloo, ON}
    \resumeItemListStart
        \resumeItem{Conveyed accountability and organization skills by managing a fund and official files as administrative manager.}
        \resumeItem{Coordinated with executive members to promote academic resources such as Open House, and Resume Critique.}
        % \resumeItem{Exercised strategized marketing and coordinated logistics while promoting academic resources for the greater Kitchener-Waterloo community.} 
        \resumeItem{Exercised strategized marketing while promoting academic resources for the greater Waterloo community.} 
        % \resumeItem{Demonstrated creativity and dedication by providing innovative suggestions and critical feedback at weekly committee meetings.}
        \resumeItem{Demonstrated creativity and dedication by providing innovative suggestions at weekly committee meetings.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Project Manager}{September 2021 - May 2022}
      {National Honour Society}{}
      \resumeItemListStart
        \resumeItem{Conducted a project of sending Christmas presents to children in Mongolia by cooperating with an organization called Samaritan’s Purse as a member of National Honour Society of my school.} 
        \resumeItem{Collected presents from 12 classes in the school and sent 100 boxes to children that are in need in Mongolia.} 
      \resumeItemListEnd

    \resumeSubheading
      {Captain of Varsity Soccer Team/Leader of Futsal Club}{February 2020 - May 2022}
      {BIS}{South Korea}
      \resumeItemListStart
        \resumeItem{Led the high school varsity soccer team as a \textbf{captain} for 3 months, by fostering \textbf{teamwork}, organizing practices,  and guiding the team through a \textbf{competitive tournament}.} 
        \resumeItem{Managed a club of 24 students by arranging teams and conflicts, and playing futsal for 30 minutes each week.} 
        \resumeItem{Recognized for outstanding performance with the MVP award for being the best player on the varsity team and the All-Star Conference honor, given to the best players in the league.} 
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd